Filling in the Gaps: Using Consumer Products to Replace Missing Pollution Data

### 2022-03-07 1_introduction.tex

The remainder of this article is organized as follows. Section \ref{background} briefly reviews the history of air quality standard in the US and some key details of current regulations. Section \ref{data} then discusses the data used and section \ref{emprical} describes the theoretical and empirical framework that will be applied to estimate the missing pollution and effects on reference levels for national standards. Section \ref{results} reviews the results of the empirical study and concludes.

>>>>

The remainder of this article is organized as follows. Section \ref{background} briefly reviews the history of air quality standard in the US and some key details of current regulations. Section \ref{data} then discusses the data used and section \ref{theoretical} describes the theoretical and empirical framework that will be applied to estimate the missing pollution and effects on reference levels for national standards. Section \ref{results} reviews the results of the empirical study and concludes.

### 2022-03-07 paper.tex

% Research Question
[abstract here]

@@

I also estimate the 95\% lower and upper bound on each predicted value; $\low$ and $\up$ to later using in lower and upper bounds on the design value.

@@

These unremarkable results for the annual design value bias are fairly representative of the batch of 15 sites. When we look at the hour design value results, we can see in 2020 and 2021, there were fairly large and significant differences between the design values. This indicates that having more restrictive data collection standards could have increased Fresno's design value significantly in these quarters. Because OLS was used to impute the missing values, we would expect the hourly imputed values to be unbiased on average. Since we are taking 3-year averages, it seems plausible to believe most bias in the imputation method would average out. These combined with the lower bounds being well above zero suggest there was indeed under-reporting of pollution in Fresno. I cannot say whether or not that it happened intentionally or by mere chance of turning off the monitor at times that would likely have recorded higher pollution.

Is this meaningful for Fresno though? Fresno has had a nonattainment status for many years and is listed on several lists within this literature as having notable pollution measurement issues. So though Fresno's recorded design value would have been higher, they were already well over the 24-hour design threshold of 35 $\mu$g/m$^3$, having pseudo design values in the 50s and 60s in 2020 and 2021.

@@

\textbf{Future Work}
\begin{itemize}
    \item I have only tested 15 of 388 possible sites. Now that I have written the bulk of the code the manage the data, most of the future work lies in acquiring the rest of the data for the NAAQS monitors and PurpleAir monitors.
    \item I am in the process of negotiating a data usage agreement with PurpleAir staff to get the entire historical dataset of all US sensors. This is the main bottleneck.
    \item I have written code to download any arbitrary NAAQS sensor data between two dates. However, some of the NAAQS monitors report on a less frequent basis than hourly, so the analysis code will need to be generalized for other reporting frequencies.
    \item I have written code to download wind velocity data, but parsing the files to get wind velocity at a particular location and time requires more work. This will be used in my predictive model for missing PM2.5 data at the NAAQS monitor.
\end{itemize}

>>>>

% Research Question
The Clean Air Act (CAA) is one of the largest-scale pollution policies in US history. Through the CAA, the National Ambient Air Quality Standards (NAAQS) provide thresholds for a basic minimum standard of air quality in the US. However, the EPA only requires 75\% completeness of air quality measurements. This minimum standard of completeness provides a plausible mechanism for locations to under-report high pollution to avoid expensive NAAQS penalties, thus biasing the air quality measurements that are compared to the NAAQS. This paper explores this issue of bias from missing data by bringing in new consumer-based outdoor air pollution data to fill in the gaps in reported data. I find that though most tested locations do not have a significant bias in their reported measurements, one of 15 sites tested has a statistically and economically large bias due to missing data that would be reported under a higher completeness standard. While this is a test on a relatively small number of NAAQS sites, this methodology can be employed in future work to examine most or all of US air quality monitors.

@@

I also estimate the 95\% lower and upper bound on each predicted value ($\low$ and $\up$) to use later in calculating lower and upper bounds on the design values for each location.

@@

These unremarkable results for the annual design value bias (columns 2-4) are fairly representative of the batch of 15 sites. When we look at the hour design value results above (columns 5-7), we can see in 2020 and 2021, there were fairly large and significant differences between the design values. This indicates that having more restrictive data collection standards could have increased Fresno's design value significantly in these quarters. Because OLS was used to impute the missing values, we would expect the hourly imputed values to be unbiased on average. Since we are taking 3-year averages, it seems plausible to believe most bias in the imputation method would average out. These combined with the lower bounds being well above zero suggest there was indeed under-reporting of pollution in Fresno. I cannot say whether or not that it happened intentionally or by mere chance of turning off the monitor at times that would likely have recorded higher pollution.

Is this meaningful for Fresno though? Fresno has had nonattainment status for many years and is listed on several lists within this literature as having notable pollution measurement issues. So though Fresno's recorded design value would have been higher, they were already well over the 24-hour design threshold of 35 $\mu$g/m$^3$, having pseudo design values in the 50s and 60s in 2020 and 2021.

@@

\textbf{Future Work}
\begin{itemize}
    \item I have only tested 15 of 388 possible sites. Now that I have written the bulk of the code to manage the data, most of the future work lies in acquiring the rest of the data for the NAAQS monitors and PurpleAir monitors.
    \item I am in the process of negotiating a data usage agreement with PurpleAir staff to get the entire historical dataset of all US sensors. This is the main bottleneck.
    \item Some of the NAAQS monitors report on a less frequent basis than hourly, so the analysis code will need to be generalized for other reporting frequencies.
    \item I have written code to download wind velocity data, but parsing the files to get wind velocity at a particular location and time requires more work. This will be used in my predictive model for missing PM2.5 data at the NAAQS monitor (see next section).
\end{itemize}
